Weighted Model Counting with Conditional Weights

### 2020-08-08 paper/paper.tex
A bug fix related to encodings

\subsection{The Space of Functions on Boolean Algebras}
% TODO: clarify why this is needed (and run a grammar check on this section)

We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. All of
these operations have efficient implementations in the CUDD
\cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
is used by ADDMC \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
multiplication and projection are as defined by \citet{DBLP:conf/aaai/DudekPV20}
while others are new.

@@

\begin{example}
  Let $U = \{a, b\}$ be a set of atoms and $\mu\colon 2^{2^U} \to
  \mathbb{R}_{\ge 0}$ a measure defined as:\footnote{The value of $\mu$ on any
    other element of $2^{2^U}$ can be deduced from the definition of a measure.}
  \begin{align*}
    \mu(a \land b) &= 0.72, \\
    \mu(a \land \neg b) &= 0.18, \\
    \mu(\neg a \land b) &= 0.07, \\
    \mu(\neg a \land \neg b) &= 0.03.
  \end{align*}
  If $\mu$ could be represented using literal-weight (factored) WMC, we would
  have to find two weight functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge
    0}$ and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu =
  \nu_a \cdot \nu_b$ induces $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to
  satisfy this system of equations:
  \begin{align*}
    \nu_a(\{a\}) \cdot \nu_b(\{b\}) &= 0.72 \\
    \nu_a(\{a\}) \cdot \nu_b(\emptyset) &= 0.18 \\
    \nu_a(\emptyset) \cdot \nu_b(\{b\}) &= 0.07 \\
    \nu_a(\emptyset) \cdot \nu_b(\emptyset) &= 0.03,
  \end{align*}
  which has no solutions.

@@

% TODO: To follow formatting requirements, I will need to remove the
% nput command. Each figure will have to be separately compiled to a PDF (maybe
% create a Makefile for that). Look up how to scale figures. Reformat all
% colours to CMYK from RGB (in R).

@@

\section{Discussion and Conclusions}

@@

% TODO: a few optimistic parting words

>>>>

\subsection{The Space of Functions on Boolean Algebras}

We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
can be efficiently represented using ADDs. Furthermore, all of the operations
are supported by the CUDD \cite{somenzi1998cudd} package that is used by ADDMC
for ADD manipulation \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
multiplication and projection are as defined by
\citet{DBLP:conf/aaai/DudekPV20}, while others are new.

@@

\begin{example}
  Let $U = \{a, b\}$ be a set of atoms and $\mu\colon 2^{2^U} \to
  \mathbb{R}_{\ge 0}$ a measure defined as $\mu(a \land b) = 0.72$, $\mu(a \land
  \neg b) = 0.18$, $\mu(\neg a \land b) = 0.07$, $\mu(\neg a \land \neg b) =
  0.03$.\footnote{The value of $\mu$ on any other element of $2^{2^U}$ can be
    deduced from the definition of a measure.} If $\mu$ could be represented
  using literal-weight (factored) WMC, we would have to find two weight
  functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $\nu_b\colon
  2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu = \nu_a \cdot \nu_b$ induces
  $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to satisfy this system of
  equations:
  \begin{align*}
    \nu_a(\{a\}) \cdot \nu_b(\{b\}) &= 0.72 \\
    \nu_a(\{a\}) \cdot \nu_b(\emptyset) &= 0.18 \\
    \nu_a(\emptyset) \cdot \nu_b(\{b\}) &= 0.07 \\
    \nu_a(\emptyset) \cdot \nu_b(\emptyset) &= 0.03,
  \end{align*}
  which has no solutions.

@@

% TODO: (needed to follow formatting requirements)
% 1. Remove the \input command.
% 2. R should compile the tex files to be standalone.
% 3. Edit the tex files to replace RGB colours with CMYK.
% 4. Compile the tex files to PDFs.
% 5. Include the PDFs (look up how to do that in the formatting guidelines).

@@

\section{Discussion and Conclusion}

@@
